Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-27 edubots_surveys.Rnw
OK, I give up
More attempts. It's around here
fixes typo in tables, again stable version

% ************************ New alaysis ***********************

@@

The reference mapping for the feature names in the experiments is in Table \ref{tab:feature_mapping}.

\begin{table}

\begin{tabular}{|c|c|}
\hline
\# Variable & Name \\
\hline
0 & AgendaBot	\\
1 & ClassMaterialBot		\\
2 & Age		\\
3 & Experience		\\
4 & FAQBot		\\
5 & GradesBot		\\
6 & Gender		\\
7 & MessagingPlatform0ne		\\
8 & MessagingPlatformOther		\\
9 & MessagingPlatformProvided		\\
10 & MessagingPlatformSlack		\\
11 & MessagingPlatformTelegram		\\
12 & MessagingPlatformWhatsApp		\\
13 & OtherBot		\\
14 & Sector		\\
15 & Messaging Organization → Number of approaches considered		\\
16 & Degrees → Number of degrees involved		\\
17 & Discipline		\\
\hline
Output & PostCOVID changes	\\
\hline
\end{tabular} \label{tab:feature_reference} \caption{Mapping of feature numbers to survey questions.}
\end{table}

@@

\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
\# Variable & Name & MI (considering one variable) & Max Relevance & mRMR\\
\hline
0 & AgendaBot	&  &  &\\
1 & ClassMaterialBot &	&  &	\\
2 & Age	&		&  &  \\
3 & Experience &			&  &  	\\
4 & FAQBot &			&  &  	\\
5 & GradesBot &			&  &  	\\
6 & Gender &			&  &  	\\
7 & MessagingPlatform0ne &			&  &  	\\
8 & MessagingPlatformOther &			&  &  	\\
9 & MessagingPlatformProvided	&			&  &  \\
10 & MessagingPlatformSlack	&			&  &  \\
11 & MessagingPlatformTelegram	&			&  &  \\
12 & MessagingPlatformWhatsApp	&			&  &  \\
13 & OtherBot	&			&  &  \\
14 & Sector	&			&  &  \\
15 & Messaging Organization → Number of approaches considered	&			&  &  \\
16 & Degrees → Number of degrees involved	&			&  &  \\
17 & Discipline	&		&  &  	\\
\hline
% Output & \multirow{3}{PostCOVID changes} & 	\\
\hline
\caption{Mapping of feature numbers to survey questions.}
\label{tab:feature_results}
\end{tabular}
\end{table}

@@

All the authors have contributed to the study presented in this manuscript. 
JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
PAC has...
AMM has ...
FB has...
NA has...
OT has...
AG has...
All authors read and approved the final manuscript.

>>>>

% ********************** ALBERTO HERE ****************************
% ************************ New analysis ***********************

@@

The reference mapping for the feature names in the experiments is in Table \ref{tab:feature_mapping}. 
\begin{table}
\begin{tabular}{|c|c|}
\hline
\# Variable & Name \\
\hline
0 & AgendaBot	\\
1 & ClassMaterialBot		\\
2 & Age		\\
3 & Experience		\\
4 & FAQBot		\\
5 & GradesBot		\\
6 & Gender		\\
7 & MessagingPlatform0ne		\\
8 & MessagingPlatformOther		\\
9 & MessagingPlatformProvided		\\
10 & MessagingPlatformSlack		\\
11 & MessagingPlatformTelegram		\\
12 & MessagingPlatformWhatsApp		\\
13 & OtherBot		\\
14 & Sector		\\
15 & Messaging Organization $\rightarrow$ Number of approaches considered		\\
16 & Degrees $\rightarrow$ Number of degrees involved		\\
17 & Discipline		\\
\hline
Output & PostCOVID changes	\\
\hline
\end{tabular}
\caption{Mapping of feature numbers to survey questions.}
\label{tab:feature_reference} 
\end{table}

@@

\begin{table}
\begin{tabular}{|c|c|c|c|c|}
\hline
\# Variable & Name & MI (considering one variable) & Max Relevance & mRMR\\
\hline
0 & AgendaBot	&  &  &\\
1 & ClassMaterialBot &	&  &	\\
2 & Age	&		&  &  \\
3 & Experience &			&  &  	\\
4 & FAQBot &			&  &  	\\
5 & GradesBot &			&  &  	\\
6 & Gender &			&  &  	\\
7 & MessagingPlatform0ne &			&  &  	\\
8 & MessagingPlatformOther &			&  &  	\\
9 & MessagingPlatformProvided	&			&  &  \\
10 & MessagingPlatformSlack	&			&  &  \\
11 & MessagingPlatformTelegram	&			&  &  \\
12 & MessagingPlatformWhatsApp	&			&  &  \\
13 & OtherBot	&			&  &  \\
14 & Sector	&			&  &  \\
15 & Messaging Organization $\rightarrow$ Number of approaches considered	&			&  &  \\
16 & Degrees $\rightarrow$ Number of degrees involved	&			&  &  \\
17 & Discipline	&		&  &  	\\
\hline
% Output & \multirow{3}{PostCOVID changes} & 	\\
\hline
\end{tabular}
\caption{Mapping of feature numbers to survey questions.}
\label{tab:feature_results}
\end{table}

@@

All the authors have contributed to the study presented in this manuscript. 
JJM has been the leader, drafted the first versions of the survey and supervised the writing of the manuscript.
PAC has...
AMM has ...
FB has...
NA has...
OT has...
AG has...
All authors have read and approved the final manuscript.
